The Chemistry Development Kit (CDK): atom typing, rendering, molecular formulas, and substructure searching

### 2016-10-09 article.tex
Last glance of the conclusion section

Since the last CDK publication in 2006, the library has been improved
in many aspects including architecture, new functionality and improved
code testing, management and deployment. These changes have led a more
functionally rich cheminformatics library, with significant
performance improvements. Updates on the common SMILES and molfile
formats and the improved structure diagram generation are very visible
and benefit many of the tools using the CDK.  Furthermore, the
stability of the development model has significantly improved,
providing greater stability of the library over time. The project
adopted peer review and quality control.

With more than 90 contributors, a long list of tools based on the CDK, and
hundreds of article citations, the CDK is alive and kicking.

>>>>

Since the second CDK publication, in 2006, the library has been improved
in many aspects including architecture, new functionality, improved
code testing, management, peer review, and deployment. These changes have led a more
functionally rich cheminformatics library, with significant
performance improvements. Updates on the common SMILES and molfile
formats and the improved structure diagram generation are very visible
and benefit many of the tools using the CDK.  Furthermore, the
stability of the development model has significantly improved,
providing greater stability of the library over time.
With more than 90 contributors, a long list of tools based on the CDK, and
hundreds of article citations, the CDK is alive and kicking.
